---
title: "Pulse Rate"
author: Rishi Sandrana
format: html
editor: visual
---

What is the difference in pulse rate between two randomly selected female students in this class?

## Wisdom

Model: Predictive

Units: Female Students in this Class

Covariates: None

Treatment: None

Outcome: Pulse Rate

Validity: The pulse rate could be calculated differently in the nhanes data and the classroom depending on the device used to measure pulse rate. Everyone's pulse rate in the classroom could be comparatively higher due to nervousness as opposed to people in the nhanes data set who may be calmer.

## Justice

Stability: A higher sugar content in peoples' diets today may imply that our class has a higher average pulse rate compared to people in 2012. (Social media and COVID also have an effect on stability.)

Representativeness: nhanes data is only for the United States but we have students from numerous places around the world.

Unconfoundedness: Not applicable because we are not using a causal model (no treatment).

Formula: pulse ~ 1

```{r}
#| echo: false
#| message: false
#| warning: false
library(tidyverse)
library(primer.data)
library(rstanarm)
```

```{r}
#| echo: false
x <- nhanes |>
  select(gender, pulse) |>
  filter(gender == "Female") |>
  drop_na()

fit_obj <- stan_glm(
  data = x,
  family = gaussian,
  refresh = 0,
  formula = pulse ~ 1,
  seed = 9
)
```

## Courage

```{r}
#| echo: false
fit_obj |> 
  as_tibble() |>
  ggplot(aes(x = `(Intercept)`)) + 
  geom_histogram(
    aes(y = after_stat(count/sum(count))),
    bins = 50,
    color = "white"
  ) +
  labs(
    title = "Posterior for Average Female Pulse Rate",
    x = expression(mu),
    y = "Probability"
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_classic()
```

## Temperance

```{r}
#| echo: false
newobs <- tibble(.rows = 2)
pp <- posterior_predict(object = fit_obj, newdata = newobs) |>
  as_tibble() |>
  rowwise() |>
  mutate(diff = abs(`2` - `1`))

pp |>
  ggplot(aes(x = diff)) + 
  geom_histogram(
    aes(y = after_stat(count/sum(count))),
    bins = 50,
    color = "white"
  ) +
  labs(
    title = "Posterior for Pulse Rate Difference Among Two Random Females",
    x = "Pulse Difference",
    y = "Probability"
  ) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_classic()
```

```{r}
#| echo: false
#| message: false
median <- median(pp$diff)
```

## Conclusion

The difference in pulse rate between two randomly selected female students is `r median`.
